### 2021-02-01 README.Rmd

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 16 / 2,
  fig.height = 9 / 2,
  message = FALSE,
  warning = FALSE,
  cache = FALSE
)
```

@@

We present an example analysis using toy data pre-loaded into the package where we will

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 16 / 2,
  fig.height = 9 / 2,
  message = FALSE,
  warning = FALSE,
  cache = FALSE
)
set.seed(76)
```

@@

We present an example analysis using toy data pre-loaded into the package where we will:
